Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-22 MS_revised.tex
moved figure legends

@@

\begin{figure}[h]
\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}
Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

@@

@@

@@

@@

\section*{Figure legends}
{\bf Figure 1. Results of the MEDUSA analysis run on the maximum
clade credibility tree from Wahlberg et al. (2009)} Rate shifts were estimated for the
following nodes (besides the background rate): 1) root, 2) Limenitidinae +
Heliconiinae, 3) \emph{Ypthima}, 4) \emph{Charaxes}, 5) Ithomiini in
part, 6) Satyrinae, 7) Coenonymphina 8) Phyciodina in part, 9) Danaini in
part, 10) \emph{Coenonympha}, 11) \emph{Caeruleuptychia} +
\emph{Magneuptychia}, 12) \emph{Callicore} + \emph{Diaethria}, 13)
Satyrina, 14) Mycalesina, 15) \emph{Pedaliodes}, 16) \emph{Dryas} +
\emph{Dryadula}, 17) \emph{Taenaris}, 18) Pseudergolinae, 19)
\emph{Anaeomorpha} + \emph{Hypna}. Circles on
nodes indicate the diversification shift number as found by MEDUSA.
Numbers next to circles indicate the posterior probability values for
such nodes.

{\bf Figure 2. Diversification rates for taxa estimated by MultiMEDUSA on
the samples of 1000 random trees}

{\bf Figure 3. Results of MultiMEDUSA analysis showing the
probability of specific nodes being characterized by significant shifts
in diversification rate}

{\bf Figure 4. BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants} Speciation and net diversification
rates are significantly higher in Solanaceae feeders (speciation rate =
$\lambda1$, net diversification rate = $r1$).

>>>>

\begin{figure}[h]
\caption{{\bf Results of the MEDUSA analysis run on the maximum
clade credibility tree from Wahlberg et al. (2009)}. Rate shifts were estimated for the
following nodes (besides the background rate): 1) root, 2) Limenitidinae +
Heliconiinae, 3) \emph{Ypthima}, 4) \emph{Charaxes}, 5) Ithomiini in
part, 6) Satyrinae, 7) Coenonymphina 8) Phyciodina in part, 9) Danaini in
part, 10) \emph{Coenonympha}, 11) \emph{Caeruleuptychia} +
\emph{Magneuptychia}, 12) \emph{Callicore} + \emph{Diaethria}, 13)
Satyrina, 14) Mycalesina, 15) \emph{Pedaliodes}, 16) \emph{Dryas} +
\emph{Dryadula}, 17) \emph{Taenaris}, 18) Pseudergolinae, 19)
\emph{Anaeomorpha} + \emph{Hypna}. Circles on
nodes indicate the diversification shift number as found by MEDUSA.
Numbers next to circles indicate the posterior probability values for
such nodes.}
\label{fig1}
\end{figure}

@@

@@

\begin{figure}[h]
\caption{{\bf Diversification rates for taxa estimated by MultiMEDUSA on
the samples of 1000 random trees}}
\label{fig2}
\end{figure}

@@

\begin{figure}[h]
\caption{{\bf Results of MultiMEDUSA analysis showing the
probability of specific nodes being characterized by significant shifts
in diversification rate}}
\label{fig3}
\end{figure}

@@

\begin{figure}[h]
\caption{{\bf BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants}.
Speciation and net diversification
rates are significantly higher in Solanaceae feeders (speciation rate =
$\lambda1$, net diversification rate = $r1$}
\label{fig4}
\end{figure}

@@
